Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2021-12-29 analysis/paper/paper.Rmd
updated some citations

Quantifying mortality associated with piscine predation in upstream habitats of the Salmon River is of particular interest for spring/summer Chinook Salmon in the Upper Salmon major population group (MPG). The Salmon River was historically the most productive tributary for spring/summer Chinook Salmon in the Columbia River basin [@Nemeth1999], but those populations have become depleted in recent decades. Currently, the Upper Salmon MPG supports eight independent, extant spring/summer Chinook Salmon populations, including Salmon River (above Redfish Lake Creek), Valley Creek, Yankee Fork Salmon River, East Fork Salmon River, Salmon River (mainstem below Redfish Lake Creek), Pahsimeroi River, Lemhi River, and North Fork Salmon River [@NOAA2017]. The Upper Salmon MPG are stream-type Chinook Salmon and exhibit two distinct migration tactics; downstream rearing (DSR) and natal reach rearing (NRR) [@Copeland2014]. Diversity of migration tactics provides a mechanism for coping with adverse conditions in freshwater rearing and migration environments and buffers against catastrophic events, thereby increasing population resiliency. Because the Deadwater Slough supports rearing for DSR migrants and is part of the migration corridor for NRR migrants, and juveniles from all Upper Salmon populations must rear in or migrate through it, it represents a significant habitat for the Upper Salmon MPG.

>>>>

Quantifying mortality associated with piscine predation in upstream habitats of the Salmon River is of particular interest for spring/summer Chinook Salmon in the Upper Salmon major population group (MPG). The Salmon River was historically the most productive tributary for spring/summer Chinook Salmon in the Columbia River basin [@Nemeth1999], but those populations have become depleted in recent decades. Currently, the Upper Salmon MPG supports eight independent, extant spring/summer Chinook Salmon populations, including Salmon River (above Redfish Lake Creek), Valley Creek, Yankee Fork Salmon River, East Fork Salmon River, Salmon River (mainstem below Redfish Lake Creek), Pahsimeroi River, Lemhi River, and North Fork Salmon River [@NOAA2017]. The Upper Salmon MPG are stream-type Chinook Salmon and exhibit two distinct migration tactics; downstream rearing (DSR) and natal reach rearing (NRR) [@Copeland2014a]. Diversity of migration tactics provides a mechanism for coping with adverse conditions in freshwater rearing and migration environments and buffers against catastrophic events, thereby increasing population resiliency. Because the Deadwater Slough supports rearing for DSR migrants and is part of the migration corridor for NRR migrants, and juveniles from all Upper Salmon populations must rear in or migrate through it, it represents a significant habitat for the Upper Salmon MPG.
